Democratizing MPC

### 2017-10-05 OaklandSubmission/eval.tex
minor

A binary linear classifier is one of the simplest classifers. Here, the input data point $x\in\R^d$
and the model is a vector $w\in\R^d$. The possible labels $\ell\in\{\mathit{true},\mathit{false}\}$
and the classifier $C_w\equiv w^Tx>0$, where $T$ denotes the matrix transpose operator.
This classifier requires $n$ multiplications, $n-1$ additions, and a comparison.

@@

A decision tree of size $N$ takes as input $x\in\R^n$ and the model consists of a boolean predicate
assigned to each internal node of the tree. In particular, a node $j\in[N]$ at depth $i$ has a predicate $b_{j}^i\equiv x_i\leq w_i$. We start evaluating the tree from the root and if the predicate at the current node $b_j^i$ is false (true) then $x$ is passed to the left (right) node $b_{2j+1}^{i+1}$ ($b_{2j+2}^{i+1}$). This process is repeated till we reach a leaf. The leaves of the tree have labels and the output label is the leaf visited by this traversal.
Such a (binary) decision tree can be encoded as a polynomial and then prediction
reduces to polynomial evaluation. E.g., a binary tree with depth one and size $N=3$ can be encoded as the polynomial
$(1-b(x))\ell_1 + b(x)\ell_2$ where $b(x)$ is the predicate at the root, $\ell_1$ is the label of the left leaf and $\ell_r$ is the label of the right leaf.

The next class of classifiers that we discuss are deep neural nets or DNNs. 
A DNN has multiple layers that each compute a matrix multiplication followed by
an {\it activation} function. The most common activation functions are 
squaring $f(x)=x^2$ and ReLU $f(x)=\mathit{max}(x,0)$. 
If $A$ is a matrix then the output of $f(A)$ is also a matrix that contains $f$  applied
 to each entry of $A$ pointwise.
Given an input vector $x$, the predicted label of a DNN is
\[
 \mathit{argmax} W_n\cdot f_{N-1}(\ldots f_1(W_1\cdot x)\ldots)
\]
Here, $W_i$'s are matrices that are part of the model and $f_i$'s are the activation functions.
The operator $\cdot$ denotes a matrix multiplication.
Neural nets usually have one or more fully connected layers.
These layers multiply a matrix with a vector.
Some neural nets have convolution layers and these are called CNNs.
For the purpose of this paper, a convolution can be considered as a (heavy) matrix-matrix multiplication. The size of matrices manipulated by convolution layers grows linearly with {\it window size} (typically 9 or 25) and the number of {\it output channels} (typically 16, 32, or 64).
Therefore, fully connected layers are easier computation-wise compared
to convolution layers. Such DNNs and CNNs are computationaly heavy but provide
much better accuracies on computer vision tasks than the classifiers discussed above.

>>>>

A binary linear classifier is one of the simplest classifers. Here, the input data point $x\in\R^d$
and the model is a vector $w\in\R^d$. The possible labels $\ell\in\{\mathit{true},\mathit{false}\}$
and the classifier $C_w\equiv w^Tx>0$, where $\cdot^T$ denotes the matrix transpose operator.
This classifier requires $n$ multiplications, $n-1$ additions, and a comparison.

@@

A decision tree of size $N$ takes as input $x\in\R^n$ and the model consists of a boolean predicate
assigned to each internal node of the tree. In particular, a node $j\in[N]$ at depth $i$ has a predicate $b_{j}^i\equiv x_i\leq w_i$. We start evaluating the tree from the root and if the predicate at the current node $b_j^i$ is false (true) then $x$ is passed to the left (right) node $b_{2j+1}^{i+1}$ ($b_{2j+2}^{i+1}$). This process is repeated till we reach a leaf. The leaves of the tree are labels and the output label is the leaf visited by this traversal.
Such a (binary) decision tree can be encoded as a polynomial and then prediction
reduces to polynomial evaluation. E.g., a binary tree with depth one and size $N=3$ can be encoded as the polynomial
$(1-b(x))\ell_1 + b(x)\ell_2$ where $b(x)$ is the predicate at the root, $\ell_1$ is the label of the left leaf and $\ell_r$ is the label of the right leaf.

The next class of classifiers that we discuss are deep neural nets or DNNs. 
A DNN has multiple layers that each compute a matrix multiplication followed by
an {\it activation} function. The most common activation functions are 
squaring $f(x)=x^2$ and ReLU $f(x)=\mathit{max}(x,0)$. 
If $A$ is a matrix then the output of $f(A)$ is also a matrix that contains $f$  applied
 to each entry of $A$ pointwise.
Given an input vector $x$, the predicted label of a DNN is
\[
 \mathit{argmax} W_n\cdot f_{N-1}(\ldots f_1(W_1\cdot x)\ldots)
\]
Here, $W_i$'s are matrices that are part of the model and $f_i$'s are the activation functions.
The operator $\cdot$ denotes a matrix multiplication.
Neural nets usually have one or more fully connected layers.
These layers multiply a matrix with a vector.
Some neural nets have convolution layers and such DNNs are also called CNNs.
For the purpose of this paper, a convolution can be considered as a (heavy) matrix-matrix multiplication. The size of matrices manipulated by a convolution layer grows linearly with {\it window size} (typically 9 or 25), the number of {\it output channels} (typically 16, 32, or 64),
and the size of the matrix input to this layer. 
Therefore, fully connected layers are easier computation-wise compared
to convolution layers. Such DNNs and CNNs are computationaly heavy but provide
much better accuracies on computer vision tasks than the classifiers discussed above.
